\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage[normalem]{ulem}
\usepackage{soul,color}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit,positioning,shapes.symbols,chains,shapes.geometric,shapes.arrows,calc}
% Copyright
\setcopyright{none}

\input{annotations}

\begin{document}

\title{BlueBridge: Pushing Shared Memory Management into the Network}


\author{Fabian Ruffy}
\affiliation{%
  \institution{University of British Columbia}
}
\email{fruffy@cs.ubc.ca}

\author{Amanda Carbonari}
\affiliation{%
  \institution{University of British Columbia}
}
\email{acarb95@cs.ubc.ca}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TO DO%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. Fix citations --> shouldn't always be in line (see Related Works)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{abstract}
% \fr{needs work}
% With the onsets of cheaper memory, datacenters can now house denser memory servers. This changes how applications can leverage in-memory processing, they now have a large bank of memory available to them. A distributed shared memory system can aid in the development of these applications by providing a single virtual address space for the application to operate on. But, distributed shared memory's main disadvantages are the complexity of concurrency, complexity of tracking data migration, and communication overhead. Current network trends, such as RDMA and Infiniband, reduce the overhead of communication, which leaves the complexity of management as the main blocking factor for distributed shared memory systems.  

Distributed shared memory (DSM) systems have been well explored, but never managed to reach widespread adoption due to the complexity involved in building them. Instead of attempting to use or build a complex DSM system, programmers opted to control the messaging semantics of their applications. An increasing trend of in-memory computation and change in datacenter programming models has led to a resurgence of DSM. Disaggregated racks require the application to reason about shared memory in order to leverage the large amount of memory in a dedicated server. DSM systems can improve the programmability of these applications, but all the management complexity inherent to DSM systems must still be addressed.

To mitigate this complexity, we propose BlueBridge, a network managed shared memory system which stores every memory address as an IPv6-compliant address. This allows the location information of memory to be encoded in the IPv6 header, which the switch can operate on, effectively moving the directory service to the switch. With the global knowledge of where memory resides and the traffic information, the controller can now manage access, migration, and concurrency of the memory.

We realize BlueBridge with an initial proof of concept implementation, which shows that IPv6 memory addressing is possible. When evaluating this implementation, we show that we can achieve a 2x reduction in latency per remote page access and, with RDMA, we can achieve latencies similar to local disk access. These numbers are not concrete representations of the speed up BlueBridge can achieve, rather they show the promise of what a fully optimized system can achieve. 
\end{abstract}

\keywords{Distributed Shared Memory, Software-Defined Networks, Remote Memory}


\maketitle

\input{intro}
% \input{background}
\input{relatedworks}
\input{overview}
\input{implementation}
\input{eval}
% \input{discussion}
\input{conclusion}

% \section{Acknowledgements}
% Thanks to Mihir for advice and guidance throughout this project and paper writing process.

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper} 

\end{document}
